An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/trans.tex
update trans

\begin{table}
  \begin{tabular}{| l |  l |}
    \hline
    Type & Operation  \\ \hline
    Integer & $X = Y, X\neq Y, X \leq Y, X < Y, X * Y < Z, \ldots $\\ \hline
    String & $\textsf{substr}(U, V), \textsf{prefix}(U,V), \textsf{suffix}(U,V), \ldots$   \\ \hline
    File Path & $\textsf{isFile}(F), \textsf{isDir}(D),\ldots$   \\ \hline
    Size & Similar to integers   \\ \hline
    Port & $P_1 > P_2$ \\ \hline
    IP Addr.  & $\textsf{sameSubnet}(addr1, addr2)$   \\

    \hline
  \end{tabular}
\caption{Table of types used in \app together with templates associated to every type}
\label{table:kysymys}
\end{table}

@@

For an entry, we denote the corresponding guard by $g(e)$, the key by $k(e)$, the value by $v(e)$, and the  
type list by $typelist(e)$.

>>>>

\begin{table}
  \begin{tabular}{| l |  l |}
    \hline
    Type &  Template \\ \hline
    Integer & $X = Y, X\neq Y, X \leq Y, X < Y, X * Y < Z, \ldots $\\ \hline
    String & $\textsf{substr}(U, V), \textsf{prefix}(U,V), \textsf{suffix}(U,V), \ldots$   \\ \hline
    File Path & $\textsf{isFile}(F), \textsf{isDir}(D),\ldots$   \\ \hline
    Size & Similar to integers   \\ \hline
    Port & $P_1 > P_2$ \\ \hline
    IP Addr.  & $\textsf{sameSubnet}(addr1, addr2)$   \\

    \hline
  \end{tabular}
\caption{Table of types, along with associated templates, used in \app}
\label{table:kysymys}
\end{table}

@@

For an entry, we denote the corresponding guard by $g(e)$, the key by $k(e)$, the value by $v(e)$, and the probabilistic
type list by $typelist(e)$.
